The instability of variational quantum mechanics with Gaussian approximants is (not) entirely due to the unstable least squares problem

### 2013-06-17 paper.tex
semi-implicit win

The stability region of the explicit Euler formula is ?.  This means ?.

>>>>

The stability region of the explicit Euler formula is the disk $|\bar k-(-1)|≤1|$.  So it is unstable for any Jacobian with complex eigenvalues, which is certainly the case for a Hamiltonian.  The implicit Euler formula, 
$$v^{n+1}=vⁿ+τf^{n+1},$$
has the opposite stability region.  For the oscillator, this becomes
$$c^{n+1}=cⁿ-iτ〈N|{H\over\hbar}|N〉c^{n+1},$$
so $c^{n+1}$ satisfies the linear equation
$$(1+iτ〈N|{H\over\hbar}|N〉)c^{n+1}=cⁿ.$$
This is still diagonal for the quartic oscillator.  To order $τ$, the implicitn formula is the same as the explicit one.  Obviously the higher powers of $τ$ make the difference when $τ$ is finite.

The results of the backward Euler formula are the opposite of the Euler formula.  Instead of increasing, the amplitudes of the larger number states decrease nearly to zero.  This distorts the trajectory of $〈a(t)〉$, as show below.

A third method is the semi-implicit one, with the formulae
$$v^{\prime n}=vⁿ+½τf^{\prime n}\qquad v^{n+1}=vⁿ+τf^{\prime n}.$$
With the Hamiltonian, this becomes
$$c^{n+1}=cⁿ-iτH\biggl(1+{iτ\over 2}H\biggr)^{-1}cⁿ.$$
